Data Exploration and Correction

### 2024-04-08 analysis/documents/2-data-exploration.qmd
fix date

# Fixing error 
# TODO make it more explicit
# image_data[image_data$date_time==max(image_data$date_time, na.rm = T),] |> View()
image_data[image_data$ymd=="2024_Aug_19",]$date_time <- lubridate::as_date("2022-08-19")
image_data[image_data$ymd=="2024_Aug_19",]$ymd <- "2024_Aug_19"

>>>>

# Fixing error 
# TODO make it more explicit
# image_data[image_data$date_time==max(image_data$date_time, na.rm = T),] |> View()
image_data[image_data$ymd=="2024_Aug_19",]$date_time <- lubridate::as_date("2022-08-19")
image_data[image_data$ymd=="2024_Aug_19",]$ymd <- "2022_Aug_19"
